Titeln på avhandlingens språk

### 2023-04-06 body/part1/chapter2-relatedwork/key_contributions.tex
notes

\section{Scope \& overview of the included publications}

@@

>>>>

\section{Overview of the contributions of this dissertation}

\todo[inline]{
    first main contribution: introduce the idea of emulating the physical part of a CPS when it comes to experimental evaluation running over an integrated communication and computation infrastructure.
    when we do that, we avoid many of the complications of experimental evaluation of these systems
    in combination with Ainur, is a very elegant proposition
    what is not currently captured precisely is that the approach is for the whole system (app + infra)
    Need to mention the emulation
    elegant and contemporary approach to efficient and repeatable evaluation of CPS

    second contribution:
    question of to which degree the emulation needs to capture certain details of the physical world?
    to which degree is emulation ``good enough''?
    for WCA specifically we propose a relatively detail of human user behavior based on empirical data
    evaluate to which extent the emulation is ``good enough'' by optimization of these systems

    Mention software, then we are on the safe.
}

\todo[inline]{Rework and rewrite.}

@@

% \section{Key contributions}

% \begin{enumerate}
%     \item A methodology for the benchmarking of latency-sensitive, feedback-loop applications enabled by Edge Computing.
%     This methodology is validated by example through representative use-cases, \gls{WCA} and \glspl{NCS}.
%     \begin{description}
%         \item[Novelty:] This is the first formalized method for this challenge in literature.
%     \end{description}

%     \item An exploration and characterization of the optimization potential of \gls{WCA} applications using the methodology, in particular with respect to sampling strategies and resulting resource and energy consumption profiles.
%     \begin{description}
%         \item[Novelty:] the study of \gls{WCA} in literature has, so far, focused primarily on prototyping applications and platforms.
%         To the best of our knowledge, only a limited subset of works~\cite{chen2017empirical,wang2019towards,wang2020scaling} deal with the performance characterization of these applications.
%         Additionally, only~\cite{wang2019towards,wang2020scaling} present heuristics for resource consumption optimization in \gls{WCA}, but no formal mathematical derivation of optimums is performed.
%     \end{description}

%     \item Tools for the implementation of the methodology, including end-to-end emulation frameworks for \gls{WCA} and \glspl{NCS} as well as a tool for Edge Computing testbed automation.
%     \begin{description}
%         \item[Novelty:] to the best of our knowledge, EdgeDroid is the first work in literature dealing with the dynamic emulation of \gls{XR} applications in networked contexts.
%         Existing works are either completely forgo the networking aspect our use rigid, deterministic workloads which fail to capture the feedback-loop interactions between system responsiveness and human behavior.

%         Likewise, \gls{CLEAVE} is the first tool for fully softwarized end-to-end emulation of generic \glspl{NCS} employing Edge and Cloud-native technologies.
%         Most other experimental approaches to \gls{NCS} research either fully simulate the system or employ real physical control systems.
%         Although a number of works exist employing a similar network-in-the-loop approach, they limit their functionality to specific control system use cases such as smart grid control, and do not represent general approaches.
%         They also do not employ Cloud or Edge-native technologies.

%         Finally, Ainur represents the first framework for Edge Computing testbed research with end-to-end automation and orchestration.
%         Existing approaches have focused primarily on achieving feature-parity with public clouds and targeting large-scale deployments, and have forgone the end-to-end automation aspect of Edge Computing experimentation.
%         Ainur is the first toolkit able to configure a testbed from scratch, run experiments, collect the data, and clean up afterwards in an automated fashion.
%     \end{description}
% \end{enumerate}

### 2023-04-06 body/part1/chapter2-relatedwork/relatedwork.tex
wooork
notes

\section{Related work}

\subsection{Emulation in \glsfmtshort{XR} research}

\subsection{Edge and Cloud Benchmarking}

@@

\subsection{Experimental research in \glsfmtshortpl{NCS}}

\subsection{Testbed research in Edge Computing}

@@

>>>>

\section{State of the art}

\subsection{Performance evaluation of Edge Computing systems}

\todo[inline]{
    Needs some massaging.
}
\todo[inline]{
    Right now includes only experimental approaches.
    Need to add mathematical models (ask James for citations) and simulations.
}

@@

\subsubsection{Testbed research in Edge Computing}

@@

\subsection{Experimental research in \glsfmtshort{MAR} and \glsfmtshort{CPS}}

\todo[inline]{
    At this point we have settled for experimental approach.
    No need to delve deep in math models and simulations, right?
}

\todo[inline]{
    Also, title again needs reworking.
}

\subsubsection{Experimental approaches to \gls{MAR} research}\label{sec:relwork:xremulation}
\todo[inline]{Rework to talk more generally about experimental research in MAR?}

\subsubsection{Experimental approaches to research in \glsfmtshortpl{NCS}}
\todo[inline]{
    Rework.
    Don't focus on repeatability argument.
    Argue that a generic front-end-emulated approach is needed for flexibility.
}

### 2023-04-06 body/part1/chapter2-relatedwork/scope.tex
notes

\section{Scope of this work}

This dissertation presents a methodology for the study of feedback-loop \gls{CPS} systems deployed on Edge Computing and studies its potential applications and implications.
This methodology is based on the emulation of the desired application workload on top of the actual Edge infrastructure, including backend computing hardware and network technology used for client-server communication.
We do not in any way claim that this methodology is the best approach to studying these systems, but rather that it is a valid approach able to produce accurate, representative results.

The scope of \gls{CPS} systems is vast and diverse, making it unfeasible to investigate all possible variations of these systems in this work. 
Instead, we opt to study a representative subset of future applications that could potentially leverage Edge Computing resources to provide innovative solutions: \gls{WCA} and \glspl{NCS}.
By considering these two application domains, we demonstrate the applicability of our methodology and showcase its efficacy.

Specifically, a subset of the research works included in this dissertation presents and studies the application of our methodology for \gls{WCA}.
To limit the scope of our research in this area, we constrain our work to \emph{step-based task-assistance} \gls{WCA}, and no other categories of \gls{WCA} are considered.
We focus on this category for a couple of reasons.
Step-based task-assistance \gls{WCA} were among the first categories of \gls{WCA} to be developed~\cite{chen2015early}, and thus represent a more mature application class compared to other \glspl{WCA}.
These applications also feature a linear mode of execution, simplifying emulation, and their step-based nature makes the tasks easier to shorten or extend for experimental purposes.
The specific application used for these studies corresponds to the LEGO assistant devised by \citeauthor{chen2015early}\cite{chen2015early}.

A separate subset of the research presented in this work discusses a preliminary foray into the applications of our methodology for \glspl{NCS}.
Given the vastness and complexity of this field, we limit our exploration to simple, small-scale, single-plant systems.
In particular, the system used as a representative example for the effectiveness of our approach for \glspl{NCS} corresponds to the \gls{2D} inverted pendulum, using simple \gls{PD} and \gls{PID} controllers.

Finally, this dissertation also briefly discusses Edge Computing testbed research and automation as an ancillary contribution to the methodology.
Our work in this domain is limited to small-scale testbeds with up to a few dozen nodes, leveraging \glspl{SDR} paired with general-purpose \gls{COTS} compute hardware.
We do not target large-scale testbeds due to their complexity, both in terms of hardware and software.

>>>>

\section{Scope of the thesis}

\todo[inline]{Write}

\begin{enumerate}
    \item Performance evaluation.
    \item \gls{CPS} and \gls{MAR}
    \item Edge Computing 
\end{enumerate}
